---
title: "US_align_report_TMscore"
output: html_notebook
---

## Reading in data from csv files

```{r warning=FALSE, paged.print=TRUE}
setwd("C:/Users/noahh/OneDrive - Uppsala universitet/Erasmus Oslo/01_Project/04_Data/TM_score_USalign_RMSD")

#Formatting the tables an reading in the csv
file_names<- list.files(,pattern=".csv")
names_col <- c("PDBchain1","PDBchain2","TM1","TM2","RMSD","ID1","ID2","IDali","L1",	"L2","Lali")

list_of_tables <- list()
k=1
for (name in file_names) {
  
  name_table <- read.csv(name, col.names = names_col)
  list_of_tables[[k]] <- name_table
  k=1+k
  }
names(list_of_tables) <- file_names
remove(name_table,names_col,name,k, file_names)
```
***
- Info: You should use TM-score normalized by length of the reference structure, here normally TM1 !
- BUT, for comparison of NON-crystal structures both values can be used.
- list entry name: First name vs second name = TM1 , second name vs first = TM2; e.g. ABB_AF2_H = ABB = structure 1 = ref for TM1, AF2 = structure 2 = ref for TM2
***
```{r warning=FALSE}
# Package names
packages <- c("ggplot2", "plyr","dplyr", "ggsignif")# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}# Packages loading
invisible(lapply(packages, library, character.only = TRUE))


```

```{r echo=TRUE}
list_input <- list(list_of_tables$crystal_ABB_H.txt.csv,
                   list_of_tables$crystal_AF2_H.txt.csv,
                   list_of_tables$crystal_IgFold_H.txt.csv,
                   list_of_tables$ABB_AF2_H.txt.csv,
                   list_of_tables$ABB_IgFold_H.txt.csv,
                   list_of_tables$AF2_IgFold_H.txt.csv )

Prepare_data <- function(list_input){
input <- join_all(dfs = list_input,by = "PDBchain1")
#if more comparisons are added just add name
type <-  c("crystal_ABB", "crystal_AF2", "crystal_IgFold","ABB_AF2", "ABB_IgFold","AF2_IgFold", "AF2_ABB", "IgFold_ABB","IgFold_AF2")
#adds classifier for boxplot
for (t in type){
  input[t] <- rep(t, times=nrow(input))
}

df_k <- data.frame(matrix(ncol = 4, nrow = 0))
colnames(df_k) <- c("PDBchain", "TM_score","RMSD", "classifier")
df_f <- data.frame(matrix(ncol = 4, nrow = 0))
colnames(df_k) <- c("PDBchain", "TM_score","RMSD", "classifier")
#first round for "crystal_ABB", "crystal_AF2", "crystal_IgFold","ABB_AF2", "ABB_IgFold","AF2_IgFold"
# if more comparisons are added just increase the loop number
for (i in 0:5){
  tm = 3+(i*10)
  rmsd = 5+(i*10)
  classifier =62+i
  df_k[1:nrow(input),c(1,2,3,4)] <- input[,c(1,tm,rmsd,classifier)]
  df_f <- rbind(df_f, df_k)
}
# second round for "AF2_ABB", "IgFold_ABB","IgFold_AF2"
# ATTENTION! if more comparisons are added the starting numbers change for tm, rmsd, and classifier.
for (i in 0:2){
  tm = 34+(i*10)
  rmsd = 35+(i*10)
  classifier =68+i
  df_k[1:nrow(input),c(1,2,3,4)] <- input[,c(1,tm,rmsd,classifier)]
  df_f <- rbind(df_f, df_k)
}
return(df_f)
}

boxplot_H_chain <- Prepare_data(list_input)
#remove(classifier, i, rmsd, t, tm, type, df_f, df_k, input, list_input )

#calculates mean, meadian and sd
summ_TM_H <- boxplot_H_chain %>% 
  group_by(classifier) %>% summarize(mean = mean(TM_score), median = median(TM_score), sd = sd(TM_score))

summ_RMSD_H <- boxplot_H_chain %>% 
  group_by(classifier) %>% 
  summarize(mean = mean(RMSD), median = median(RMSD), sd = sd(RMSD))
# colors
type2 <-  c("crystal_ABB", "crystal_AF2", "crystal_IgFold","ABB_AF2", "ABB_IgFold","AF2_IgFold", "AF2_ABB", "IgFold_ABB","IgFold_AF2") 
pers_color <- c("#A6CEE3","#92D3FF","#1F78B4", "#FB9A99", "#E31A1C", "#B2DF8A", "#33A02C", "#FDBF6F", "#FF7F00")
boxplot_H_chain$classifier <- factor(boxplot_H_chain$classifier, levels = type2)
```

# Making the heavy chain TM plots
## Violinplot heavy chain TM-score
```{r}
TM_plot <- function(boxplot_X_chain, chain_name_for_file, summ_TM_X, plot_type) {
  title_name <- paste("Plot of", chain_name_for_file, "chain prediction TM-score")
plot1 <- ggplot(boxplot_X_chain, aes(x = classifier, y = TM_score)) +
  theme_minimal()+
  scale_fill_manual(values = pers_color)+
  plot_type(aes(fill = classifier), lwd=0.4)+
  labs(title= title_name ,x="Comparison between", y = "TM-score (higher = better)")+
  theme(axis.text.x = element_text(size=7, angle=45, margin=margin(t=4), hjust = 1),
        axis.text.y = element_text(size=7))+ theme(legend.title=element_blank()) +
  stat_summary(aes(x=classifier,y = TM_score),
               fun = "mean",
               col = "black",
               size = 0.5,
               width=0.3,
               geom="errorbar",
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) +
  stat_summary(aes(x=classifier,y = TM_score),
               fun = "mean", geom = "point", size=2, shape=15) +
  #stat_summary(aes(x=crystal_ABB,y = TM1.x),
  #fun = "median", geom = "point", size=3, color="red", shape =8)
  geom_label(data = summ_TM_X, aes(x = classifier, y = 0.125, label = paste("Mean: ", round(mean, 3), "\nMedian: ",round(median, 3), "\nSD: ", round(sd, 3))), size = 2, label.size = 0, label.padding = unit(0.1, "lines")) + #Adds labels
geom_signif(aes(x=classifier, y = TM_score), comparisons = list(c("crystal_AF2", "crystal_IgFold"),
                                                                        c("crystal_ABB", "crystal_IgFold"),
                                                                        c("crystal_ABB", "crystal_AF2")),
                    map_signif_level = TRUE, y_position = c(1,1.1,1)) 
return(plot1)
}
plot1<- TM_plot(boxplot_H_chain, "heavy", summ_TM_H, geom_violin)
plot1
ggsave("Violinplot of Heavy Chain prediction TM-score.jpeg", width = 2500, height = 1500, units = "px")
```


## Boxplot heavy chain TM-score
```{r}
plot2<- TM_plot(boxplot_H_chain, "heavy", summ_TM_H, geom_boxplot)
plot2
ggsave("Boxplot of Heavy Chain prediction TM-score.jpeg", width = 2500, height = 1500, units = "px")
```

# Making heavy chain RMSD plots
## Violinplot heavy chain RMSD

```{r}
RMSD_plot <- function(boxplot_X_chain, chain_name_for_file, summ_RMSD_X, plot_type) {
  title_name <- paste("Plot of", chain_name_for_file, "chain prediction RMSD-score")
plot1 <- ggplot(boxplot_X_chain, aes(x = classifier, y = RMSD)) +
  theme_minimal()+
  scale_fill_manual(values = pers_color)+
  plot_type(aes(fill = classifier), lwd=0.4)+
  labs(title= title_name ,x="Comparison between", y = "RMSD-score (higher = worse)")+
  theme(axis.text.x = element_text(size=7, angle=45, margin=margin(t=4), hjust = 1),
        axis.text.y = element_text(size=7))+ theme(legend.title=element_blank()) +
  stat_summary(aes(x=classifier,y = RMSD),
               fun = "mean",
               col = "black",
               size = 0.5,
               width=0.3,
               geom="errorbar",
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) +
  stat_summary(aes(x=classifier,y = RMSD),
               fun = "mean", geom = "point", size=2, shape=15) +
   geom_label(data = summ_RMSD_X, aes(x = classifier, y = -0.5, label = paste("Mean: ", round(mean, 3), "\nMedian: ",round(median, 3), "\nSD: ", round(sd, 3))), size = 2, label.size = 0, label.padding = unit(0.1, "lines")) + #Adds labels
geom_signif(aes(x=classifier, y = RMSD), comparisons = list(c("crystal_AF2", "crystal_IgFold"),
                                                                        c("crystal_ABB", "crystal_IgFold"),
                                                                        c("crystal_ABB", "crystal_AF2")),
                    map_signif_level = TRUE, y_position = c(6,6.5,6))
return(plot1)
}
plot3<- RMSD_plot(boxplot_H_chain, "heavy", summ_RMSD_H, geom_violin)
plot3

ggsave("Violinplot of Heavy Chain prediction RMSD-score.jpeg", width = 2500, height = 1500, units = "px")
```
# Boxplot heavy chain RMSD
```{r}
plot4<- RMSD_plot(boxplot_H_chain, "heavy", summ_RMSD_H, geom_boxplot)
plot4

ggsave("Boxplot of Heavy Chain prediction RMSD-score.jpeg", width = 2500, height = 1500, units = "px")
```

# Light chain predictions
## Data prepeation for boxplots
- inner join between all input files to secure comperability of scoring results. The problem of non-predictability of some structures in some tools has to be evaluated in another way. 
```{r}
# Add more comparisons from list if needed
list_input <- list(list_of_tables$crystal_ABB_L.txt.csv,
                   list_of_tables$crystal_AF2_L.txt.csv,
                   list_of_tables$crystal_IgFold_L.txt.csv,
                   list_of_tables$ABB_AF2_L.txt.csv,
                   list_of_tables$ABB_IgFold_L.txt.csv,
                   list_of_tables$AF2_IgFold_L.txt.csv )

boxplot_L_chain <- Prepare_data(list_input)

#calculates mean, meadian and sd
summ_TM_L <- boxplot_L_chain %>% 
  group_by(classifier) %>% summarize(mean = mean(TM_score), median = median(TM_score), sd = sd(TM_score))

summ_RMSD_L <- boxplot_L_chain %>% 
  group_by(classifier) %>% 
  summarize(mean = mean(RMSD), median = median(RMSD), sd = sd(RMSD))
# correct colors for the plots
boxplot_L_chain$classifier <- factor(boxplot_L_chain$classifier, levels = type2)
```
# Making the light chain TM plots
## Violinplot light chain TM-score
```{r}
plot5<- TM_plot(boxplot_L_chain, "light", summ_TM_L, geom_violin)
plot5
ggsave("Violinplot of Light Chain prediction TM-score.jpeg", width = 2500, height = 1500, units = "px")
```


## Boxplot light chain TM-score
```{r}
plot6<- TM_plot(boxplot_L_chain, "light", summ_TM_L, geom_boxplot)
plot6
ggsave("Boxplot of Light Chain prediction TM-score.jpeg", width = 2500, height = 1500, units = "px")
```

# Making light chain RMSD plots
## Violinplot light chain RMSD

```{r}
plot7<- RMSD_plot(boxplot_L_chain, "light", summ_RMSD_L, geom_violin)
plot7

ggsave("Violinplot of Light Chain prediction RMSD-score.jpeg", width = 2500, height = 1500, units = "px")
```
# Boxplot light chain RMSD
```{r}
plot8<- RMSD_plot(boxplot_L_chain, "light", summ_RMSD_L, geom_boxplot)
plot8

ggsave("Boxplot of Light Chain prediction RMSD-score.jpeg", width = 2500, height = 1500, units = "px")
```
# Paired chain predictions
## Data prepeation for boxplots
- inner join between all input files to secure comperability of scoring results. The problem of non-predictability of some structures in some tools has to be evaluated in another way. 
```{r}
# Add more comparisons from list if needed
list_input <- list(list_of_tables$crystal_ABB_paired.txt.csv,
                   list_of_tables$crystal_AF2_paired.txt.csv,
                   list_of_tables$crystal_IgFold_paired.txt.csv,
                   list_of_tables$ABB_AF2_paired.txt.csv,
                   list_of_tables$ABB_IgFold_paired.txt.csv,
                   list_of_tables$AF2_IgFold_paired.txt.csv )

boxplot_Paired_chain <- Prepare_data(list_input)

 
#calculates mean, meadian and sd
summ_TM_Paired <- boxplot_Paired_chain %>% 
  group_by(classifier) %>% summarize(mean = mean(TM_score), median = median(TM_score), sd = sd(TM_score))

summ_RMSD_Paired <- boxplot_Paired_chain %>% 
  group_by(classifier) %>% 
  summarize(mean = mean(RMSD), median = median(RMSD), sd = sd(RMSD))
# correct colors for the plots
boxplot_Paired_chain$classifier <- factor(boxplot_Paired_chain$classifier, levels = type2)
```
# Making the paired chain TM plots
## Violinplot paired chain TM-score
```{r}
plot9<- TM_plot(boxplot_Paired_chain, "paired", summ_TM_Paired, geom_violin)
plot9
ggsave("Violinplot of Paired Chain prediction TM-score.jpeg", width = 2500, height = 1500, units = "px")
```


## Boxplot paired chain TM-score
```{r}
plot10<- TM_plot(boxplot_Paired_chain, "paired", summ_TM_Paired, geom_boxplot)
plot10
ggsave("Boxplot of Paired Chain prediction TM-score.jpeg", width = 2500, height = 1500, units = "px")
```

# Making paired chain RMSD plots
## Violinplot paired chain RMSD

```{r}
plot11<- RMSD_plot(boxplot_Paired_chain, "paired", summ_RMSD_Paired, geom_violin)
plot11

ggsave("Violinplot of Paired Chain prediction RMSD-score.jpeg", width = 2500, height = 1500, units = "px")
```
# Boxplot paired chain RMSD
```{r}
plot12<- RMSD_plot(boxplot_Paired_chain, "paired", summ_RMSD_Paired, geom_boxplot)
plot12
ggsave("Boxplot of Paired Chain prediction RMSD-score.jpeg", width = 2500, height = 1500, units = "px")
```
# Summary plots
```{r}

gh <- data.frame(c("mean_H", "mean_L", "mean_paired"))
rmsd_summary_df <- cbind(summ_RMSD_H$mean, summ_RMSD_L$mean, summ_RMSD_Paired$mean)
rmsd_summary_df <- data.frame(rmsd_summary_df[5:7,]) #select only crystal vs X
rmsd_summary_df$classifier <- gh$c..mean_H....mean_L....mean_paired..
names <- c( "crystal_ABB", "crystal_AF2", "crystal_IgFold", "classifier")
colnames(rmsd_summary_df) <- names
```


```{r}
remove(plot1,plot2,plot3,plot4,plot5,plot6,plot7,plot8,plot9,plot10,plot11,plot12, installed_packages,packages, type2, list_input, names, gh)
remove(summ_RMSD_Paired, summ_TM_Paired)
remove(summ_RMSD_L, summ_TM_L)
remove(summ_RMSD_H, summ_TM_H)
```

```{r eval=FALSE, include=FALSE}
write.csv(boxplot_H_chain, "data_H_chain_USalign.csv")
write.csv(boxplot_L_chain, "data_L_chain_USalign.csv")
write.csv(boxplot_Paired_chain, "data_Paired_chain_USalign.csv")

write.csv(summ_RMSD_H, "summ_RMSD_H_USalign.csv")
write.csv(summ_RMSD_L, "summ_RMSD_L_USalign.csv")
write.csv(summ_RMSD_Paired, "summ_RMSD_Paired_USalign.csv")

write.csv(summ_TM_H, "summ_TM_H_USalign.csv")
write.csv(summ_TM_L, "summ_TM_L_USalign.csv")
write.csv(summ_TM_Paired, "summ_TM_Paired_USalign.csv")
```

